\documentclass{amsart}
\usepackage{amsfonts} % For math fonts
\usepackage{amsmath, amssymb, amsthm}
\usepackage{float}
\usepackage{enumitem}
\usepackage{graphicx}
\setlist[enumerate,1]{label=\arabic*.}
\setlist[enumerate,2]{label=\alph*.,itemindent=2em}
\setlist{topsep=0pt, leftmargin=*, labelsep=1em}

\title{Week 1 CS 180}
\author{Asher Christian 006-150-286}
\date{ 06.01.25}

\begin{document}
\maketitle
\section{Day 1}
\begin{enumerate}
    \item famous\\
        a person is famous if every person in the room knows them and they no nobody.\\
        A know B? - allowed operation - yes or no\\
        optimize over the number of questions.\\
        worst case for n students to see if everyone knows one person need to ask n-1 questions.\\
        Then worst case we ask the person of interest n-1 questions to see if they know each person.\\
        $2(n-1)$ total questions.\\
        arbitrary vs random: random needs randomization (costly) (do not say randomize when mean arbitrary)\\
        repeat this process for checking famousness 2n(n-1) times but there can only be 1 or 0 famous people\\
        $2n^2-2n \sim n^2$ \\
        There are $n^2$ relationships or $n$ choose 2.\\
        If A knows B then A is not famous. If A does not know B then B is not famous.\\
        \begin{align*}
            Q &| n\\
            1 &| n-1\\
            2 &| n-2\\
            ...\\
            n-1 &| 1
        \end{align*}
        And 2(n-1) to verify if the last person is famous.
        $3(n-1)$ questions.\\
        There must be at least $n$ questions asked because otherwise there would be some person that we have no information from and which could change the outcome.\\
    \item models of computation\\
        serial model of computation - von neumman model of computation\\
        A computer with an ALU and a local register - constant\\
        ALU can do basic operations (addition, subtraction, shift right, shift left) reasonable and simple\\
        Each operation takes about 1 unit of time\\
        We assume we have a large memory that we can read and write in one unit of time.\\
        Input output takes 1 unit of time.\\
    \item $S = \sum_{i=1}^{n}x_i$\\
        Input our numbers first into register then memory takes 2n units.\\
        $x_1 \rightarrow ALU, x_2 \rightarrow ALU, +, x_3 \rightarrow ALU, +, ..., x_n \rightarrow ALU, +$\\
        2(n-1) + 1\\
        ouput + 1\\
        4n total. $\sim n$.
\end{enumerate}
\section{Day 2}
\begin{enumerate}
    \item Matching problems\\
        Given 2 groups, group A and group B with circles representing members of the group\\
        We must match a member of A with a member of B according to some rule and restrictions specified by the problem\\
        $|A| = n, |B|  = n$.
        Every member of A must be matched with 1 and exactly 1 member of B\\
    \item Stable Matching Problem\\
        Match $a_i$ with $b_i$? non-interesting.\\
        Each element of $A$ comes with a complete ranking or priority list
        \[
        a_1 \rightarrow (3, 4, 1, 2, 6, ... )
        .\] 
        The first element is the first choice, second is second choice, etc\\
        For each $b_i$ there is a complete ranking of $A$ \\
        If there exist $a_i,a_j,b_k,b_l$ with $a_i-b_k$ and $a_j-b_l$ but $a_i$ prefers $b_l$ over $b_k$ and  $b_k$ prefers $a_i$ over $a_j$ the matching
        is unstable. If for all such sets of pairs there are no unstable matches then the matching is stable.\\
        By this definition there is always a stable configuration.\\
    \item Algorithm to solve Stable Matching Problem as above\\
        $a_i$ asks $b_k$ to match. If $b_k$ has no match it says yes and $(a_i,b_k)$ match.\\
        If $b_k$ has a match with $a_j$ if  $rank(j) > rank(i)$ then there is no match - reject the match\\
        if  $rank(i) > rank(j)$ $b_k$ says yes and it drops $a_j$ and $(a_i, b_k)$ is now a match\\
        Go to arbitrary $a$ ask to match with the highest rank $b$ not asked before. Ask to match with that $b$.
        $b$ will accept if not matched. If it does have a match it will accept only if the rank of $a$ is higher than its current match.
        There are $n$ $a's$ and each $a$ may ask at most $n$ questions so there are at most $n^2$ operations and each operation takes one unit of time so  the entire process runs in $n^2$ units of time.\\
    \item Proof\\
        Assume for contradiction that there exists an unstable matching. a matches with b and $a'$ with $b'$ but $a$ prefers $b'$ and $b'$ prefers $a$.
        $a$ must have asked $b'$ in the past because $b'$ is ranked higher than $b$ for them.
\end{enumerate}


\end{document}
