\documentclass[11pt]{article}

\newcommand{\cnum}{Math 275A}
\newcommand{\ced}{Fall 2025}
\newcommand{\ctitle}[4]{\title{\vspace{-0.5in}\cnum, \ced\\Assignment #1: #2}\author{\vspace{-0.35in}\\#3, #4}}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames,svgnames,table,hyperref]{xcolor}
\usepackage{amsmath, amsfonts}
\usepackage{graphicx} % Required for inserting images
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{comment}

\renewcommand*{\theenumi}{\alph{enumi}}
\renewcommand*\labelenumi{(\theenumi)}
\renewcommand*{\theenumii}{\roman{enumii}}
\renewcommand*\labelenumii{\theenumii.}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{header}{HTML}{205459}
\definecolor{solution}{HTML}{204d52}

\newcommand{\solution}[1]{{{\textcolor{header}{Solution:} \textcolor{solution}{#1}}}}
\setlist[enumerate]{label=(\alph*)}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}


\begin{document}
\ctitle{\#8}{}{Asher Christian}{006-150-286}
\date{}
\maketitle

\section{review}
if $f_n$ uniformly integrable and $f_n \rightarrow f$ in measure
then $f_n \rightarrow f$ in $L^{1}$ proof in textbook

\section{1.6 Differentiation theorems}
integration on $ \mathbb{R}$ 
\\
fundamental theorem of calculus
\begin{enumerate}
    \item  $f : [a,b] \rightarrow \mathbb{R}$ continuous, $F(t) = \int_{a}^{t}f(x)dx$ for all $t$.
        then $F$ differentiable on  $(a,b)$  and  $F'(x) = f(x)$ 
    \item if $F : [a,b] \rightarrow \mathbb{R}$ continuously differentiable then  $\int_{a}^{b}F'(t)dt = F(b) - F(a)$
\end{enumerate}
Suppose $f(x) = 1_{x \ge 1}$ then  $F(x) = \int_{0}^{x}f(t)dt =  \max(x-1,0)$ and
$F$ is differentiable if $x \ne 1$.\\
if  $F(x) = 1_{x \ge 1}$ then  $F'(x) = 0$ almost everywhere. but  $\int_{0}^{2}F'(t)dt = 0 \ne F(2) - F(0) = 1$\\
What can be salvaged from FTC if one has less regularity?

\section{Lebesgue differentiation theorem 1st version}
if $f : [a,b] \rightarrow \mathbb{C}, $ absolutely integrable., $F(x) = \int_{[a,x]}^{}f(t)dt$ for $x \in (a,b]$
then  $F$ is continuous everywhere and differentiable almost everywhere. for all $x \in (a,b]$ and  $y \rightarrow x, y \in (a,b]$ then $\lim_{y\to x}F(y) = F(x)$
and for almost every $x \in (a,b]$
 \[
\lim_{y\to x} \frac{F(y) - F(x)}{y-x} = f(x)
\] 
where we ensure $y \ne x $ and  $y \in (a,b]$. In other words the first fundamental theorem of calculus holds
almost everywhere for absolutely integrable functions
\solution{
    Use the dense subclass argument if $f \in L^{1}([a,b]), \epsilon > 0$, there exists $g \in C([a,b])$ such that
     \[
         ||f-g||_{L^{1}} = \int_{[a,b]}^{}|f(x)-g(x)|dx < \epsilon
    \] 
    first we want to show $F$ is continuous, let $y_n \rightarrow x$ in $[a,b]$, want to show  $F(y_n) \rightarrow F(x)$ or that
    \[
        \int_{[a,y_n]}^{}f(t)dt \rightarrow \int_{[a,x]}^{}f(t)dt
    \] 
    \[
        \int_{[a,b]}^{}1_{[a,y_n]}f(t)dt \rightarrow^{?} \int_{[a,b]}^{}f(t) 1_{[a,x]}dt
    \] 
    however the convergence is guaranteed by the dominated convergence theorem since everything is dominated by $|f|$.
    \\
    The hard part is to show that  $F'(x) = f(x)$ almost everywhere. Fix  $x \in [a,b]$, $x \ne a,b$
     \[
         F'(x) = \lim_{y\to x \; y \in (a,b], y \ne x} \frac{F(y) - F(x)}{y-x}  =^{?} f(x)
    \] 
    it sufficies to show the right limits and left limits so we focus on the right limts.
    \[
    \lim_{y\to x^{+}}\frac{F(y) - F(x)}{y-x}
    \] 
    $y = x + h,$  $h > 0$ we want
     \[
         \lim_{h\to 0^{+}}\frac{F(x+h) - F(x)}{h} = \frac{\int_{[a,x+h]}^{}f(t)dt - \int_{[a,x]}^{}f(t)dt}{h} = \frac{\int_{[x,x+h]}^{}f(t)dt}{h} =^{?} f(x)
    \] 
    want to show 
    \[
        \lim_{h\to 0^{+}}\frac{\int_{[x,x+h]}^{}f(t)dt}{h} - f(x) =^{?} 0
    \] 
    but
    \[
        f(x) = \frac{\int_{[x,x+h]}^{}f(x)dt}{h}
    \] 
    so we get
    \[
        \lim_{h\to 0^{+}} \int_{[x,x+h]}^{}\frac{f(t)-f(x)}{h}dt
    \] 
    we have by triangle inequality
    \[
        |\int_{[x,x+h]}^{}\frac{f(t)-f(x)}{h}dt| \le \int_{[x,x+h]}^{}|\frac{f(t)-f(x)}{h}| dt
    \] 
    by squeeze it suffices to show that
    \[
        \limsup_{h\to 0^{+}} \int_{[x,x+h]}^{}|\frac{f(t)-f(x)}{h}| dt = 0
    \] 
    by change of variables $t = x + hy, dt = hdy$ can rewrite as
    \[
        \int_{[0,1]}^{}|f(x+hy) - f(x)|dy
    \] 
    pick $\lambda > 0$ look at
    \[
        \{x : \limsup_{h\to 0} \int_{[x,x+h]}^{}|\frac{f(t)- f(x)}{h}| dt > \lambda\}
    \] 
    if we can show this set has measure 0 for all $\lambda > 0$ we are done. Fix $\epsilon > 0$
    there exists $g \in C([a,b])$ such that  $||f -g||_{L^{1}} < \epsilon$ and we know
    \[
        \lim_{h\to 0} \int_{[x,x+h]}^{}|\frac{g(t)-g(x)}{h}|dt = 0
    \]
   \[
       \frac{|f(t) - f(x)|}{h} \le \frac{1}{h}( |f(t) - g(t)|  + |g(t) - g(x)| +  |g(x) - f(x)|)
   \] 
   and so when we integrate we get the same inequality.
   but
   \[
       \int_{[x,x+h]}^{}\frac{|g(x)-f(x)|}{h}dt = |g(x) - f(x)|
   \] 
   \[
       \int_{[x,x+h]}^{}\frac{|g(t)-g(x)|}{h}dt \rightarrow 0 
   \] 
   as $h \rightarrow 0$ and we hav
   \[
       \limsup_{h\to 0^{+}}\int_{[x,x+h]}^{}\frac{|f(t)-f(x)|}{h}dt \le \limsup_{h\to 0^{+}} \int_{[x,x+h]}^{}\frac{|f(t)-g(t)|}{h}dt + |g(x) - f(x)|
   \] 
   if lhs is bigger than lambda then either of the two terms on the right is bigger than $\frac{\lambda}{2}$
   but we have
   \[
       \mu(\{x : |g(x) - f(x)| > \frac{\lambda}{2}\}) \le 2\frac{||g-f||_{L^{1}}}{\lambda} \le \frac{2\epsilon}{\lambda}
   \] 
   and we can pick $\epsilon$ as small as we wish to get this set arbitrarily small.
   we have
   \[
       \limsup_{h\to 0 } \int_{[x,x+h]}^{}\frac{|f(t)-g(t)|}{h}dt \le \sup_{h} \int_{[x,x+h]}^{}\frac{|f(t)-g(t)|}{h}dt
   \] 
   we need to use the Hardy-Littlewood maximall inequality. $f \in L^{1}( \mathbb{R})$ $\lambda > 0$ then
   \[
       m(\{x : \sup_{h > 0} \frac{1}{h} \int_{[x,x+h]}^{}|f(t)| dt \ge \lambda\}) \le \frac{||f||_{L^{1}( \mathbb{R})}}{\lambda}
   \] 
   if we prove this inequality we prove that the other term is violated one a set of measure less than $\frac{2\epsilon}{\lambda}$ and we are done so it suffices to prove this inequality.
}

\section{1D lebesgue diff thm:}

\[
    f \in L^{1}[a,b], F(x) = \int_{[a,x]}^{}f(t)dt \implies F \text{cts, diff. a.e,}
\] 
for almost every $x \in (a,b]$  $\frac{d}{dx}F(x) = f(x)$
\[
    \frac{1}{h}\int_{x}^{x+h}f(t)dt \rightarrow f(x), h \rightarrow 0^{+}, \text{a.e.}
\] 
"measurable functions are almost continuous"
Hardy-Littlewood maximal inequality 1D, one-sided $f \in L^{1}( \mathbb{R}), \lambda > 0$
\[
    m(\{x : \sup_h \frac{1}{h}\int_{x}^{x+h}|f(t)|dt \ge \lambda \}) \le \frac{\int_{}^{}|f|}{\lambda}
\] 

\section{Rising sun lemma}
\emph{
    \[
        F : [a,b] \rightarrow \mathbb{R} \text{cts}
    \] 
    then $\exists$ at most countably many disjoint interals  $(a_n,b_n) \subset [a,b]$ such that
    \begin{enumerate}
        \item on each $(a_n,b_n)$ either  $F(a_n) = F(b_n)$ or $a_n = a$,  $F(b_n) \ge F(a_n)$
        \item if  $x \not\in (a_n,b_n)$, $x \in [a,b]$ for any  $n$ then  $F(y) \le F(x)$ for all  $x \le y \le b$
    \end{enumerate}
}
skip the proof for now
but rising sun implies HL max inequality which implies lebesgue differentiation theorem
\[
    F(x) = \int_{[a,x]}^{}|f(t)|dt - \lambda(x-a)
\] 
then $F(x)$ is continuous so we can apply rising sun lemma suppose that  $x$ does not lie in the intervals
described in the lemma, then for any $h> 0$ $F(x+h) \le F(x)$ if you rearrange
\[
    \frac{1}{h}\int_{[x,x+h]}^{}|f(t)|dt \le \lambda
\] 
so the set where this is big is less than or equal to  $\sum_{}^{}|b_n - a_n|$
for any $a_n,b_n$ not  $a_n = a$ then 
 \[
     F(b_n) = F(a_n) \implies \int_{[a_n,b_n]}^{}|f(t)|dt - \lambda(B_3 - a_3)
\] 
\[
    \int_{[a,b]}^{}|f(t)dt \ge \int_{\bigcup [a_n,b_n]}^{}|f(t|dt = \lambda \sum_{}^{}(b_n - a_n)
\] 

\section{Lebesgue differentiation thm}
\[
f \in L^{1}( \mathbb{R}^{d})
\] 
\emph{
    for almost every $x$ 
    \[
        \lim_{r\to 0} \frac{1}{m(B(x,r))}\int_{B(x,r)}^{}f(t)dt = f(x)
    \] 
    and additionally
    \[
        \frac{1}{m(B(x,r))} \int_{B(x,r)}^{} |f(t) - f(x)| dt \rightarrow 0 \text{as $r \rightarrow 0$}
    \] 
}
this proof is also derived from a HL max inequality on
\[
    m(\{x : \sup_{r} \frac{1}{m(B(x,r))}\int_{B(x,r)}^{}|f(t)|dt > \lambda\}) \le C_d \frac{\int_{}^{}|f|dt}{\lambda}
\] 
where $C_d$ is a constant depending only on  $d$.
Covering lemma
\section{Covering lemma}
\emph{
    $B_1, \dots, B)n$ balls in $ \mathbb{R}^{d}$ (not necessarily disjoint) then there exists
    a subcollection $B_1', \dots, B_m'$ which are disjoint that 
    \[
        \bigcup_{i=1}^{n}B_i \subset \bigcup_{j=1}^{m}3B_j'
    \] 
}

Question? under what conditions $f : [a,b] \rightarrow \mathbb{R}$ can we saythat $\int_{[a,b]}^{}f'(t)dt = f(b) - f(a)$ we know this holds if $f \in C^{1}$
Suppose $f$ is monotone increasing on $[a,b]$ then  $f$ is continuous almost everywhere except on a countable set. $f$ is also differentiable almost everywhere (rising sun lemma on $f(t) - \lambda t$).
so we can integrate $\int_{}^{}f'(t)$ we get
\[
    \int_{[a,b]}^{}f'(t)dt \le f(b) - f(a)
\] 
uses fatou's lemma.

counter example, cantor function "devil's staircase" continuous monotone increasing, differentiable almost everywhere  $f'(t) = 0$

\section{absolute continuity}
$f$ is absolutely continuous if for every $\epsilon$ there exists $\delta > 0$ such that if $I_1,I_2,\dots,I_n$ disjoint intervals
with $\sum_{}^{}|I_i| \le \delta$ then it implies $\sum_{}^{}|f(I_i)| \le \epsilon$
if $f$ is abs continuous then $f$ is differentiable almost everywhere and
\[
    \int_{[a,b]}^{}f'(t)dt = f(b) - f(a)
\] 
if $f$ is integrable and $F(x) = \int_{[0,x]}^{}f(t)dt$ is absolutely continuous
\end{document}
