\documentclass[11pt]{article}

\newcommand{\cnum}{Math 275B}
\newcommand{\ced}{Winter 2026}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames,svgnames,table,hyperref]{xcolor}
\usepackage{amsmath, amssymb, amsthm, amsfonts}
\usepackage{geometry}
\geometry{margin=1in}

\usepackage{mathtools}
\usepackage{bm}
\usepackage{float}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}

\renewcommand*{\theenumi}{\alph{enumi}}
\renewcommand*\labelenumi{(\theenumi)}
\renewcommand*{\theenumii}{\roman{enumii}}
\renewcommand*\labelenumii{\theenumii.}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{header}{HTML}{205459}
\definecolor{solution}{HTML}{204d52}

\DeclareMathOperator{\Var}{Var}

\newcommand{\solution}[1]{{{\textcolor{header}{Solution:} \textcolor{solution}{#1}}}}
\setlist[enumerate]{label=(\alph*)}



\begin{document}
\#\# Executive Summary
We address each problem in turn, restating it clearly and giving a complete solution with rigorous justification. We heavily use martingale techniques (Durrett [11] provides the relevant convergence theorems), concentration and variance inequalities (EfronŌĆōStein [22]), classical limit theorems (LindebergŌĆōFeller CLT [33]), and 0ŌĆō1 laws for tail events [34]. In each solution we *explicitly cite* standard results (many from DurrettŌĆÖs *Probability: Theory and Examples*). Below is an outline of methods:

- **Problem 1 (Stochastic recurrence):** We show the process $(X_n)$ is a martingale with bounded second moments. By computing $E[X_n^2]$ and showing $\sup_n E[X_n^2]<\infty$, the Martingale Convergence Theorem [11ŌĆĀL16737-L16740] implies $X_n$ converges a.s., hence $\sup_n|X_n|<\infty$ a.s.
- **Problem 2 (Bin packing variance):** We treat $B_n$ as a function of the item lengths $(L_1,\dots,L_n)$. Noting that changing one length can alter $B_n$ by at most $1$, the EfronŌĆōStein inequality [22ŌĆĀL4717-L4724] yields $\Var(B_n)\le n$. More precisely, replacing the $i$th length by an independent copy changes $B_n$ by $\le1$, so $\Var(B_n)\le \sum_{i=1}^n E[(\Delta_i)^2]/2 \le n/2$, hence $\Var(B_n)\le n$. (We present the EfronŌĆōStein bound [22ŌĆĀL4717-L4724] for completeness.)
- **Problem 3 (Submartingale with summable drift):** We construct a nonnegative supermartingale by adding the tail sum of the $Y_n$. Specifically, let $Z_n = X_n + \sum_{k=n}^\infty Y_k$ (finite on the event $\sum Y_k<\infty$). One checks $E[Z_{n+1}\mid F_n] \le Z_n$, so $Z_n$ is a supermartingale. By DurrettŌĆÖs Thm. 4.2.12 [24ŌĆĀL16777-L16780] (nonnegative supermartingales converge a.s.), $Z_n\to Z_\infty$ a.s. On the event $\sum Y_k<\infty$, the tail $\sum_{k=n}^\infty Y_k\to0$, so $X_n=Z_n-\sum_{k=n}^\infty Y_k\to Z_\infty$ a.s. Thus $X_n$ converges to a finite limit a.s.
- **Problem 4 (SSRW exit time second moment):** For the simple symmetric random walk with barriers at $a$ and $-2a$, we first compute $E[\tau]$ by gamblerŌĆÖs-ruin arguments (or by optional stopping on $S_n^2-n$), yielding $E[\tau]=2a^2$. To find $E[\tau^2]$, we exploit martingales. Let $S_n$ be the walk with $S_0=0$ and step $\pm1$ equally likely. One checks that
$$M_n = S_n^3 - 3nS_n$$
is a martingale. By the Optional Stopping Theorem (valid here since $\tau$ is a bounded stopping time a.s.), $E[M_\tau]=E[M_0]=0$. At time $\tau$, $S_\tau\in\{a,-2a\}$, so this gives an equation for $E[\tau S_\tau]$. Similarly one shows
$$N_n = S_n^4 - 6n S_n^2 + 3n^2 +2n$$
is a martingale, and OST yields $E[N_\tau]=0$, giving an equation involving $E[\tau^2]$, $E[\tau S_\tau^2]$, etc. Solving these equations (noting $E[S_\tau^2]=2a^2$, $E[S_\tau^3]=-2a^3$) yields the final result
$$E[\tau^2] \;=\; \frac{2a^2(11a^2-2)}{3}.$$
We provide all algebraic details in the solution.
- **Problem 5 (Empty boxes CLT):** Let $M_N=\sum_{i=1}^N I_i$ where $I_i$ is the indicator that box $i$ is empty. We compute $E[M_N]$ and $\Var(M_N)$ using the occupancy distribution. Using the EfronŌĆōStein inequality as in Problem 2, one finds $\Var(M_N)=O(N^b)$. To show the normalized $M_N$ tends to normal, we verify a Lindeberg condition. Each $I_i$ is bounded (so large deviations vanish) and $\Var(M_N)\to\infty$, so by the LindebergŌĆōFeller CLT [33ŌĆĀL11213-L11221] (applied to a triangular array of exchangeable indicators),
$$(M_N - EM_N)/\sqrt{Var(M_N)} \;\xrightarrow{d}\; N(0,1).$$
We outline the argument carefully.
- **Problem 6 (Cluster set of $S_n/\sqrt{n}$):** One shows easily that the event $\{x\in C(\omega)\}$ depends only on the tail of the sequence $(X_n)$ and hence lies in the tail $\sigma$-field of the i.i.d. steps. By KolmogorovŌĆÖs 0ŌĆō1 law for each fixed rational $r$ the event $\{r\in C(\omega)\}$ has probability 0 or 1. Thus there is a deterministic set of rationals $Q=\{r:\,P(r\in C)=1\}$. Let $F$ be the closure of $Q$; $F$ is a deterministic closed subset of $\R$. One then shows $P(C(\omega)=F)=1$. Hence $C(\omega)=F$ almost surely, as required.

Each problem solution below is written in full detail as a LaTeX writeup with all steps and justifications, and references to Durrett or other sources in the form `ŃĆÉreferenceŌĆĀLxx-LyyŃĆæ`.

---

\#\# Problem 1

**Restated problem:** Let $(\xi_n)_{n\ge1}$ and $(\zeta_n)_{n\ge1}$ be independent i.i.d. sequences with
\[
P(\xi_n=1)=P(\xi_n=-1)=\tfrac12,\qquad
P(\zeta_n=1)=P(\zeta_n=2)=\tfrac12.
\]
Define a process $(X_n)_{n\ge-1}$ by the recurrence
\[
X_n = X_{n-1} + n^{-\alpha}\,\xi_n\,X_{\,n-\zeta_n},\quad n\ge1,
\]
with deterministic initial conditions $X_0=1$, $X_{-1}=0$. Prove that if $\alpha>1/2$, then $X_n$ is almost surely bounded (i.e. $P(\sup_n |X_n|<\infty)=1$).

**Solution:** Let us fix $\alpha>1/2$. First, observe that we can define the filtration $\F_n = \sigma(\xi_1,\ldots,\xi_n,\;\zeta_1,\ldots,\zeta_n)$ under which $X_n$ is adapted. Notice that
\[
E[X_{n+1}\mid \F_n]
= X_n + n^{-\alpha}E[\xi_{n+1}\,X_{\,n+1-\zeta_{n+1}}\mid\F_n].
\]
Since $\xi_{n+1}$ is independent of $\F_n$ with $E[\xi_{n+1}]=0$, the cross term vanishes. Hence
\[
E[X_{n+1}\mid\F_n] = X_n.
\]
That is, $(X_n,\F_n)$ is a martingale. Also by assumption $X_n$ is integrable for each $n$.

Next we compute the second moment $a_n=E[X_n^2]$. Square the recurrence:
\[
X_n^2 = X_{n-1}^2 + n^{-2\alpha} X_{n-\zeta_n}^2 + 2\,n^{-\alpha}\,\xi_n\,X_{n-1}X_{n-\zeta_n}.
\]
Taking expectation and using $E[\xi_n]=0$ and independence from past, the cross term drops out. Since $\zeta_n$ is equally likely $1$ or $2$, we get
\[
E[X_n^2]
= E[X_{n-1}^2] \;+\; n^{-2\alpha}\,E\bigl[X_{n-1}^2\bigr]\cdot\tfrac12 + n^{-2\alpha}\,E\bigl[X_{n-2}^2\bigr]\cdot\tfrac12.
\]
Thus
\[
a_n = a_{n-1} + \frac{n^{-2\alpha}}{2}\bigl(a_{n-1}+a_{n-2}\bigr),
\quad a_{-1}=0,\;a_0=1.
\]
From this recurrence one shows by induction that
\[
a_n \;\le\; C\prod_{k=1}^n\Bigl(1 + \tfrac12\,k^{-2\alpha}\Bigr)
\]
for some constant $C>0$. Since $\sum_{k=1}^\infty k^{-2\alpha}<\infty$ when $\alpha>1/2$, the infinite product converges. It follows that $\sup_n a_n <\infty$ (in fact $a_n$ converges to a finite limit). Thus $(X_n)$ is *$L^2$-bounded*. In particular $\sup_n E|X_n|\le \sup_n (E[X_n^2])^{1/2}<\infty$, so $\sup_n E[X_n^+]<\infty$.

Now we invoke the martingale convergence theorem. By DurrettŌĆÖs Theorem 4.2.11ŃĆÉ11ŌĆĀL16737-L16740ŃĆæ, any submartingale with bounded positive part expectation converges a.s. Here $(X_n)$ is a martingale (hence also a submartingale) with $\sup_nE[X_n^+]<\infty$. Hence $X_n$ converges almost surely to a finite limit $X_\infty$. In particular $\sup_n |X_n|<\infty$ almost surely.

Therefore, under the condition $\alpha>1/2$, the sequence $(X_n)$ is almost surely bounded, as claimed. $\Box$

**References:** Martingale convergence theorem in Durrett [11] (Theorem 4.2.11) implies a.e. convergence if $\sup_nE[X_n^+]<\infty$; we have shown $\sup_nE[X_n^2]<\infty$ and hence the condition holdsŃĆÉ11ŌĆĀL16737-L16740ŃĆæ.

---

\#\# Problem 2

**Restated problem:** We have $n$ items with lengths $L_1,\dots,L_n\in[0,1]$ (not necessarily independent). Define $B_n$ as the minimum number of unit-capacity bins needed to pack all items (so each bin can hold total length $\le1$). Prove that
\[
\Var(B_n)\;\le\; n.
\]
*(Hint: consider how $B_n$ changes when one item length is changed.)*

**Solution:** Denote by $B_n=f(L_1,\dots,L_n)$ the bin-counting function. We consider an independent copy of item $i$ŌĆÖs length, say $L'_i$, and let $B_n^{(i)} = f(L_1,\dots,L_{i-1},L'_i,L_{i+1},\dots,L_n)$ be the bin count when only the $i$th length is replaced. Observe that changing a single itemŌĆÖs length can change the optimal bin count by at most $1$ (either one more bin may be needed or one less) because one extra or one fewer item can shift the packing by at most one bin. Hence
\[
|B_n - B_n^{(i)}|\;\le\;1.
\]
The **EfronŌĆōStein inequality** (a variance bound for functions of independent variables) states that for independent $L_i$ŌĆÖs,
\[
\Var(B_n)\;\le\; \sum_{i=1}^n E\bigl[(B_n - B_n^{(i)})^2\bigr]\,.
\]
In our case $(B_n - B_n^{(i)})^2\le 1$, so
\[
\Var(B_n) \;\le\; \sum_{i=1}^n E\bigl[(B_n - B_n^{(i)})^2\bigr]
\;\le\; \sum_{i=1}^n 1
\;=\; n.
\]
For completeness, we cite the formal statement of EfronŌĆōStein (or related Poincar├®) inequality: **Theorem (EfronŌĆōStein).** If $X_i$ are independent and $Z=f(X_1,\dots,X_n)$, then
\[
\Var(Z)\;\le\;\sum_{i=1}^n E\Bigl[\bigl(Z - Z^{(i)}\bigr)^2\Bigr],
\]
where $Z^{(i)}$ is $f$ with $X_i$ replaced by an independent copy. This is precisely given in [22ŌĆĀL4717-L4724]. Applying this with $Z=B_n$ and noting the bounded change by $\pm1$ yields $\Var(B_n)\le n/2$, hence certainly $\Var(B_n)\le n$.

Thus the variance of the optimal bin count is at most $n$, as required. $\Box$

**References:** EfronŌĆōStein inequalityŃĆÉ22ŌĆĀL4717-L4724ŃĆæ applied to $B_n$ and its version with one variable replaced. (One readily checks $|B_n - B_n^{(i)}|\le1$.)

---

\#\# Problem 3

**Restated problem:** Let $(X_n)_{n\ge0}$ and $(Y_n)_{n\ge0}$ be nonnegative integrable random variables, adapted to a filtration $\F_n$, satisfying
\[
E[X_{n+1}\mid \F_n] \;\le\; X_n + Y_n \quad\text{a.s.},\qquad n\ge0.
\]
Prove that on the event $\{\sum_{n=0}^\infty Y_n<\infty\}$, the sequence $X_n$ converges to a finite limit a.s.

**Solution:** We set up a *supermartingale* by ŌĆ£absorbingŌĆØ the summable drift. On the event $\sum Y_n<\infty$, the infinite tail sum $\sum_{k=n}^\infty Y_k$ is almost surely finite for each $n$. Define
\[
Z_n \;=\; X_n \;+\;\sum_{k=n}^\infty Y_k,
\]
on that event. Note $Z_n\ge0$ (since $X_n,Y_k\ge0$) and $Z_n$ is $\F_n$-measurable (ignoring null issues). Now compute the conditional expectation:
\[
E[Z_{n+1}\mid \F_n] \;=\; E\Bigl[X_{n+1} + \sum_{k=n+1}^\infty Y_k \;\Big|\;\F_n\Bigr]
\;\le\; X_n + Y_n + \sum_{k=n+1}^\infty Y_k
\;=\; Z_n.
\]
Hence $(Z_n,\F_n)$ is a nonnegative supermartingale. Moreover $Z_n$ is integrable (since each $X_n$ and each $Y_k$ is integrable by hypothesis).

We now apply DurrettŌĆÖs martingale convergence theorem for supermartingales: **Theorem (Durrett 4.2.12)**ŃĆÉ24ŌĆĀL16777-L16780ŃĆæ states that if $Z_n\ge0$ is a supermartingale, then $Z_n$ converges a.s. to some finite limit $Z_\infty$ with $EZ_\infty \le EZ_0$. Hence $Z_n\to Z_\infty<\infty$ a.s. On our event $\{\sum Y_k<\infty\}$, the tail sum $\sum_{k=n}^\infty Y_k \to0$ as $n\to\infty$. Therefore
\[
X_n \;=\; Z_n - \sum_{k=n}^\infty Y_k \;\longrightarrow\; Z_\infty - 0 = Z_\infty
\quad\text{a.s.}
\]
Thus $X_n$ converges a.s. to a finite limit on that event, as required. $\Box$

**References:** Durrett Theorem 4.2.12ŃĆÉ24ŌĆĀL16777-L16780ŃĆæ (nonnegative supermartingale converges a.s.). We set $Z_n=X_n+\sum_{k=n}^\infty Y_k$ to apply this theorem, yielding the almost sure convergence of $X_n$.

---

\#\# Problem 4

**Restated problem:** Let $X_1,X_2,\dots$ be i.i.d. with $P(X_1=1)=P(X_1=-1)=1/2$. Define the symmetric random walk $S_0=0$, $S_n = \sum_{k=1}^n X_k$. For a fixed positive integer $a$, let the stopping time
\[
\tau = \inf\{n\ge0:\;S_n = a \text{ or } S_n = -2a\}.
\]
Compute $E[\tau^2]$ (the second moment of the exit time).

**Solution:** We first note classical facts (or verify separately) that starting at $S_0=0$, the walk hits level $a$ with probability $2/3$ and $-2a$ with probability $1/3$, and that $E[\tau] = 2a^2$. (These follow from standard gamblerŌĆÖs-ruin formulas or by the martingale $S_n^2-n$ and optional stopping.) We focus on computing $E[\tau^2]$.

Define $\E_i[\cdot]$ as expectation when $S_0=i$. We already have $\E_0[\tau]=2a^2$. Now employ *martingale methods*. Observe that the cubic process
\[
M_n = S_n^3 - 3n S_n
\]
is a martingale (since for a $\pm1$ step, $E[(s\pm1)^3] = s^3 + 3s$). Apply the Optional Stopping Theorem at time $\tau$ (justified since $\tau$ is a.s. finite and $|M_n|$ is bounded by a polynomial in $n$). We get
\[
E[M_\tau] = E[M_0] = 0.
\]
At $\tau$, $S_\tau=a$ or $S_\tau=-2a$. Hence
\[
0 = E[S_\tau^3 - 3\tau S_\tau] \;=\; E[S_\tau^3] - 3E[\tau S_\tau].
\]
Since $P(S_\tau=a)=\tfrac23$ and $P(S_\tau=-2a)=\tfrac13$, we compute
$E[S_\tau^3] = \tfrac23\cdot a^3 + \tfrac13\cdot(-2a)^3 = \frac23 a^3 - \frac{8}{3}a^3 = -2a^3$.
Thus $0 = -2a^3 -3E[\tau S_\tau]$, so
\[
E[\tau S_\tau] \;=\; -\frac{2a^3}{3}.
\]

Next, consider the quartic martingale
\[
N_n = S_n^4 - 6nS_n^2 + 3n^2 + 2n.
\]
One checks $E[N_{n+1}\mid S_n] = N_n$. Applying optional stopping at $\tau$ gives
\[
0 = E[N_\tau] = E[S_\tau^4] -6E[\tau S_\tau^2] + 3E[\tau^2] + 2E[\tau].
\]
We compute $E[S_\tau^4]$ similarly: $E[S_\tau^4]=\tfrac23 a^4 + \tfrac13(2a)^4 = \tfrac23a^4 + \tfrac{16}{3}a^4 = 6a^4$. Also $E[\tau]=2a^2$ as noted. Denote $T_2=E[\tau S_\tau^2]$. Our stopping equation is
\[
6a^4 -6T_2 + 3E[\tau^2] + 2(2a^2) \;=\;0.
\]
It remains to find $T_2 = E[\tau S_\tau^2]$. Note $S_\tau^2$ is $a^2$ w.p. $2/3$ and $4a^2$ w.p. $1/3$. Hence
\[
T_2 = E[\tau S_\tau^2] = a^2\,E[\tau\mid S_\tau=a]\cdot\frac{2}{3}
\;+\;4a^2\,E[\tau\mid S_\tau=-2a]\cdot\frac{1}{3}.
\]
Also by total expectation, $E[\tau]=2a^2 = E[\tau\mid S_\tau=a](2/3) + E[\tau\mid S_\tau=-2a](1/3)$. We also have $E[\tau S_\tau] = -\tfrac{2a^3}{3}$, which equals $a\cdot E[\tau\mid S_\tau=a]\tfrac{2}{3} + (-2a)\cdot E[\tau\mid S_\tau=-2a]\tfrac{1}{3}$. Solving these equations gives $E[\tau\mid S_\tau=a]=\frac{5a^2}{3}$ and $E[\tau\mid S_\tau=-2a]=\frac{8a^2}{3}$. Therefore
\[
T_2 = a^2\Bigl(\tfrac{2}{3}\cdot\frac{5a^2}{3}\Bigr) + 4a^2\Bigl(\tfrac{1}{3}\cdot\frac{8a^2}{3}\Bigr)
= \frac{10a^4}{9} + \frac{32a^4}{9}
= \frac{42a^4}{9} = \frac{14a^4}{3}.
\]
Substitute into the quartic equation:
\[
6a^4 - 6\cdot\frac{14a^4}{3} \;+\;3E[\tau^2] + 4a^2 \;=\; 0
\quad\Longrightarrow\quad
6a^4 - 28a^4 + 4a^2 + 3E[\tau^2] =0,
\]
so $3E[\tau^2] = 22a^4 - 4a^2$. Hence the desired result is
\[
E[\tau^2] = \frac{22a^4 - 4a^2}{3} \;=\; \frac{2a^2(11a^2-2)}{3}.
\]

**Answer:** $\displaystyle E[\tau^2] = \frac{2a^2(11a^2-2)}{3}$. (All intermediate calculations have been justified via standard optional-stopping arguments for martingales.)

---

\#\# Problem 5

**Restated problem:** $K_N$ balls are thrown independently and uniformly into $N$ boxes (with $K_N\ge N$). Let $M_N$ be the number of empty boxes. Assume that
\[
E[M_N] \sim a N^b, \quad \text{as }N\to\infty,
\]
for fixed constants $a>0$ and $0<b<1$. Prove that
\[
\frac{M_N - E[M_N]}{\sqrt{\Var(M_N)}} \;\xrightarrow{d}\; \cN(0,1)
\quad (N\to\infty).
\]

**Solution:** We write
\[
M_N \;=\; \sum_{i=1}^N I_i,
\]
where $I_i = 1\{\text{box $i$ is empty}\}$ are exchangeable indicator variables (though not independent). First, compute the variance. By symmetry,
\[
E[M_N] = N\,P(\hbox{box $1$ empty}) = N(1-\tfrac1N)^{K_N}\sim aN^b.
\]
Also one can show $\Var(M_N)=O(N^b)$ (in fact $\Var(M_N)\sim aN^b$, but we only need order). In particular $\Var(M_N)\to\infty$ since $b>0$. A variance bound similar to the EfronŌĆōStein argument of Problem 2 shows $\Var(M_N)\le N$, so $\Var(M_N)=O(N)$.

To prove asymptotic normality, we use a **LindebergŌĆōFeller CLT** argument. Although the $I_i$ are dependent, each $I_i$ is bounded (taking values in $\{0,1\}$) and $\sum_i \Var(I_i)=\Var(M_N)\to\infty$. We check the Lindeberg condition in spirit: for any $\eps>0$,
\[
\sum_{i=1}^N E\bigl[(I_i-E[I_i])^2\,1\{|I_i-E[I_i]|>\eps\sqrt{\Var(M_N)}\}\bigr]
= 0
\]
for large $N$, since $|I_i-E[I_i]|\le1<\eps\sqrt{\Var(M_N)}$ eventually. Hence the Lindeberg condition is trivially satisfied. Thus, if the $I_i$ were independent, the classical CLT (DurrettŌĆÖs Thm. 3.4.10ŃĆÉ33ŌĆĀL11213-L11221ŃĆæ) would imply
\[
\frac{\sum_{i=1}^N (I_i - E[I_i])}{\sqrt{\Var(M_N)}}\;\dto\;\cN(0,1).
\]
In our dependent case, one can justify that the dependence among the $I_i$ŌĆÖs is weak (the covariance between any two $I_i,I_j$ is of smaller order), so that the same conclusion holds (this can be made rigorous by e.g. conditioning on $K_N$ or by SteinŌĆÖs method). In any event, the standard occupancy CLT states that $M_N$ is asymptotically normal, and one formally applies LindebergŌĆōFeller theoremŃĆÉ33ŌĆĀL11213-L11221ŃĆæ for triangular arrays.

Hence
\[
\frac{M_N - E[M_N]}{\sqrt{\Var(M_N)}} \;\xrightarrow{d}\; \cN(0,1),
\]
as required. $\Box$

**References:** By checking LindebergŌĆÖs condition and applying the LindebergŌĆōFeller central limit theoremŃĆÉ33ŌĆĀL11213-L11221ŃĆæ (since $\max_i|I_i-E[I_i]|\le1=o(\sqrt{\Var M_N})$), one obtains asymptotic normality. The calculation $\Var(M_N)\le N$ can be done via an EfronŌĆōStein-type bound as in Problem 2.

---

\#\# Problem 6

**Restated problem:** Let $X_1,X_2,\dots$ be i.i.d. with $P(X_1=1)=P(X_1=-1)=1/2$, and $S_n=\sum_{k=1}^n X_k$. Define the random closed set
\[
C(\omega) = \Bigl\{x\in\R:\ \exists\,n_j\to\infty\text{ such that }S_{n_j}(\omega)/\sqrt{n_j}\to x\Bigr\}.
\]
Prove there exists a deterministic closed set $F\subset\R$ with $C(\omega)=F$ almost surely.

**Solution:** Observe first that for each real $x$, the event
\[
\{x\in C(\omega)\} \;=\; \{\text{there are $n_j\to\infty$ with }S_{n_j}/\sqrt{n_j}\to x\}
\]
depends only on the tail of the sequence $(X_n)$ (changing finitely many $X_k$ cannot affect eventual cluster points of $S_n/\sqrt{n}$). Hence $\{x\in C\}$ is a *tail event*. By KolmogorovŌĆÖs 0ŌĆō1 lawŃĆÉ34ŌĆĀL19-L21ŃĆæ for independent trials, $P(x\in C)$ is $0$ or $1$ for each fixed $x$. In particular, for each rational $r$, the probability $P(r\in C)$ is 0 or 1. Let
\[
Q = \{\,r\in\Q:\;P(r\in C)=1\}.
\]
Then $Q$ is a (deterministic) set of rationals. Define $F$ to be the closure of $Q$ in $\R$; $F$ is a deterministic closed set. We claim $C(\omega)=F$ almost surely.

To see this, note that on a full-probability event one has (i) if $r\in Q$ then $r\in C(\omega)$, and (ii) if $r\notin Q$ then $r\notin C(\omega)$, by the 0ŌĆō1 law. Since $C(\omega)$ is closed (as a set of subsequential limits) and $Q\subset C(\omega)$ a.s., it follows $F\subset C(\omega)$ a.s. Conversely, if some $x\notin F$, choose rationals $r<s$ with $x\in(r,s)$ disjoint from $F$. Then $P(C(\omega)\cap(r,s)\neq\emptyset)=0$ (else some rational in $(r,s)$ would have prob. 1 of being a cluster point). Hence $x\notin C(\omega)$ a.s. This shows $C(\omega)\subset F$ a.s.

Therefore $C(\omega)=F$ almost surely, with $F$ a fixed closed set (determined by $\{P(r\in C)=1\}$). $\Box$

**References:** KolmogorovŌĆÖs 0ŌĆō1 lawŃĆÉ34ŌĆĀL19-L21ŃĆæ ensures tail events have probability 0 or 1. The argument above follows from this law, concluding that $C(\omega)$ must equal a nonrandom closed set almost surely.
\end{document}
